### 2023-02-03 definitions.tex
details

For instance, the well-known mutual exclusion property is often modelized in a $d$-counters machine by the property that a counter $c_{mutex}$ must be bounded by (usually) one. Then, the set $SAFE =  \{c_{mutex} \leq 1\} \times \mathbb{N}^{d-1}$ is downward closed and $BAD =\{c_{mutex} \geq 2\} \times  \mathbb{N}^{d-1} $ is the upward closed complementary of SAFE. In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that BAD is always downward closed and SAFE is always upward closed.
%		
In what follows, we will always suppose that a downward closed set $D$ is given by its finite set of ideals $I(D)$ satisfying $D=\downarrow D =I(D) \cap S$and that an upward closed set $U$ is given by its finite set of minimal elements, $b(U)$.

@@

\begin{proposition}\label{down-up}
Let $\mathscr{S}$ be an effective WSTS with effective predbasis and let the two finite sets $I(BAD)$ and  $b(SAFE)$ representing $\downarrow BAD$ and $\uparrow SAFE$.
The uniform resilience problem (URP), the uniform bounded resilience problem (UBRP) and the uniform $k$-resilience problem (UkRP) are decidable
\end{proposition}

\begin{proof}
The uniform resilience problem (URP) reduces to decide coverability of the finite set $b(SAFE)$ from the infinite set $BAD$; but it is sufficient to decide coverability from the finite set of maximal elements of $BAD$ which are ideals but not elements in $S$. We use the fact that y is coverable from an $x \in BAD$ iff $y$ is coverable from $x' \in I(BAD)$.

@@

>>>>

For instance, the well-known mutual exclusion property is often modelized in a $d$-counters machine by the property that a counter $c_{mutex}$ must be bounded by (usually) one. Then, the set $SAFE =  \{c_{mutex} \leq 1\} \times \mathbb{N}^{d-1}$ is downward closed and $BAD =\{c_{mutex} \geq 2\} \times  \mathbb{N}^{d-1} $ is the upward closed complementary of SAFE. In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that BAD is always downward closed and SAFE is always upward closed.
%		
In what follows, we will always suppose that a downward closed set $D$ is given by its finite set of ideals $I(D)=\{J_1, J_2,...,J_n\}$ satisfying $D=\downarrow D = S \cap \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ and that an upward closed set $U$ is given by its finite set of minimal elements, $b(U)$.

@@

\begin{proposition}\label{down-up}
Let $\mathscr{S}$ be an effective WSTS with effective predbasis and let the two finite sets $I(BAD)$ and  $b(SAFE)$ representing $\downarrow BAD$ and $\uparrow SAFE$. Let us suppose that is completion-post-effective class of WSTS.
The uniform resilience problem (URP), the uniform bounded resilience problem (UBRP) and the uniform $k$-resilience problem (UkRP) are decidable
\end{proposition}

\begin{proof}
Let $I(BAD)=\{J_1, J_2,...,J_n\}$ representing $BAD$ and  $b(SAFE)=\{b_1,b_2,...,b_m\}$ representing $SAFE$.
The uniform resilience problem (URP) reduces to decide infinite instances of the coverability problem : for all $x \in BAD$ does there exist an $j$ st $b_j$ is coverable from $x$. Let us reduce this infinite coverability questions by $n$ instances of the coverability problem from ideals but not elements in $S$: for all $i$, does there exist an $j$ st $b_j$ is coverable from $J_i$

We use the fact that y is coverable from an $x \in BAD$ iff $\downarrow y$ is coverable from $\downarrow x$ in $\hat{S}$
%' \in I(BAD)$.
\alain{à prouver}

@@

URP is decidable for lossy counter machines (LCM) as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}.
